---
title: "RMHW12"
author: "Joseph"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = 'hide)
library(tidyverse)
```

# **Pre-Class Assignment 12 - Time to Relax! Fall 25**

This assignment is associated with Chapters 11 and 12 (Salkind). 

**Always save a copy of your responses to the individual assignments before you submit them (either by taking a picture of your answers or by copying and pasting your answers into a word document). You will need them for you discussion assignment and you will not always have access to your responses after you submit them.**

**Instructions:** Research suggests that undergoing a digital detox (also sometimes called a social media detox), in which you refrain from using your phone to scroll through social media for a period of time, may help to reduce depression symptoms (Ramadhan et al., 2024). A professor wants to study this further. She measures her students ratings of generalized anxiety (on a scale from 1-10) before and after a 2 week digital detox (in which they refrain from engaging or scrolling on social media). The data are below. She expects that anxiety will decrease at the end of the 2 weeks. 

|                               |                              |
|:-----------------------------:|:----------------------------:|
| **Before Social Media Detox** | **After Social Media Detox** |
|               7               |              5               |
|               6               |              5               |
|               5               |              4               |
|               5               |              5               |
|               9               |              7               |
|              10               |              8               |
|              10               |              9               |
|               9               |              7               |
|               7               |              6               |
|               4               |              4               |
|               9               |              7               |
|               6               |              5               |
|               6               |              4               |
|               5               |              4               |
|               6               |              3               |
|               5               |              4               |

```{r}
data <- read_tsv("Before Social Media Detox	After Social Media Detox
7	5
6	5
5	4
5	5
9	7
10	8
10	9
9	7
7	6
4	4
9	7
6	5
6	4
5	4
6	3
5	4"
)

```

## 1. What's the null hypothesis for this research question?

Depression symptom scores will stay the same or increase after a social media detox,

$H_0 : \mu_{posttest} \ge \mu_{pretest}$

## 2. What's the alternative hypothesis for this research question?

Depression symptom scores will decrease after a social media detox,

$H_a : \mu_{posttest} < \mu_{pretest}$

## 3. The next step is to compute the test statistic. What is the t-statistic value (make sure you're using the t-test formula for the dependent samples t-test). Round your answer to two decimal places.

```{r}
sum_D = sum(data$`After Social Media Detox` - 
              data$`Before Social Media Detox`) # -22
n = nrow(data) # 16
sum_D2 <- sum((data$`After Social Media Detox` - 
                data$`Before Social Media Detox`)^2) # 40
t = sum_D / sqrt(
  (n*sum_D2 - sum_D^2) / (n-1)
)
t # -6.82191
t.test(data$`After Social Media Detox`, 
       data$`Before Social Media Detox`, paired = TRUE) # -6.82191
```

-6.82

## 5. What are the degrees of freedom?

16 - 1 = 15

## 6. What is the critical value?

t(15) = 1.753
